Epistemic Semantics in Guarded String Models\thanks{Thanks guys.}

### 2021-01-14 tex/pdraft.tex
Additions to grammar figure, and thanks.

\title{Epistemic Semantics in Guarded String Models\thanks{Thanks guys.}}
\renewcommand\footnotemark{}
%%\renewcommand\footnoterule{}

@@

\begin{figure}[!t]
  \vspace{1em}
  \centering
  \footnotesize
  %% \begin{tabular}[t]{lcc}
  %%   \toprule
  %%       \textsc{Item} & \textsc{Type} & \textsc{Semantics}\\ \midrule
  %%       Amy & $e$ & $\hat{R}_a$\\
  %%       Bob & $e$ & $\hat{R}_b$\\
  %%       it & $d$ & $d$ \\
  %%       heads & $d \backslash_D t$ & $\lambda x.\bullet^*h$ \\
  %%       tails & $d \backslash_D t$ & $\lambda x.\bullet^*t$ \\
  %%       is & $(d \backslash t)\slash(d \backslash_D t)$ & $\lambda P~x.~P~x$ \\
  %%       knows & $(e \backslash t)\slash_M t$ &  $\lambda p~R.~p\vee{\Diamond}_Rp$\\
  %%       believes & $(e \backslash t)\slash_M t$ &  $\lambda p~R.~{\Diamond}_Rp$\\
  %%       that  & $(((e \backslash t){\slash_M}t) \backslash (e \backslash t)) \slash t$
  %%       & $\lambda p\,m\,R.{\neg}(m\,({\neg}p)\,R)$ \\
  %%       whether  & $(((e \backslash t){\slash_M} t) \backslash (e \backslash t)) \slash t$
  %%       & $\lambda p\,m\,R.{\neg}(m\,({\neg}p)\,R)$ \\
  %%       && \multicolumn{1}{r}{$+ {\neg}(m\,p\,R)$} \\ \bottomrule
  %% \end{tabular}

  \newcommand{\hdrspc}{0.3em}
    \begin{tabular}[t]{l>{\hspace{-.8em}}c >{\hspace{-.6em}}c}
    \toprule
    \textsc{Item} & \textsc{Type} & \textsc{Semantics}\\ \midrule
    \multicolumn{3}{c}{{\bf Statives with expletive subject}} \\[\hdrspc]
        heads & $d \backslash_D t$ & $\lambda x.\,\bullet^*h$ \\
        tails & $d \backslash_D t$ & $\lambda x.\,\bullet^*t$ \\ \midrule
    \multicolumn{3}{c}{{\bf Agents}} \\
        Amy & $e$ & $\hat{R}_a$\\
        Bob & $e$ & $\hat{R}_b$\\ \midrule
    \multicolumn{3}{c}{{\bf Auxiliary verbs and expletive subjects}} \\[\hdrspc]
        it & $d$ & {\em{dummy}} \\
        is & $(d \backslash t)\slash(d \backslash_D t)$ & $\lambda P\,x.\,P\,x$ \\
        it's & $(t \slash(d \backslash_D t)$ & $\lambda P\,x.\,P\,x$ \\
        isn't & $t\slash(d \backslash_D t)$ & $\lambda P\,x.\,\neg P\,x$ \\
        doesn't & $(e \backslash t)\slash(d \backslash_V t)$ & $\lambda P\,x.\,\neg P\,x$ \\  \midrule
    \multicolumn{3}{c}{{\bf Tensed attitude verbs}} \\[\hdrspc]
        knows & $(e \backslash t)\slash_M t$ &  $\lambda p\,R.\,p + {\Diamond}_Rp$\\
        believes & $(e \backslash t)\slash_M t$ &  $\lambda p\,R.\,{\Diamond}_Rp$\\ \midrule
    \multicolumn{3}{c}{{\bf Base form attitude verbs}} \\[\hdrspc]
        know & $(e \backslash_V t)\slash_M t$ &  $\lambda p\,R.\,p + {\Diamond}_Rp$\\
        believe & $(e \backslash_V t)\slash_M t$ &  $\lambda p\,R.\,{\Diamond}_Rp$\\ \midrule
    \multicolumn{3}{c}{{\bf Complementizers}} \\[\hdrspc]
        that  & $(((e \backslash t){\slash_M}t) \backslash (e \backslash t)) \slash t$
        & $\begin{pmatrix*}[l]
          \lambda p\,m\,R.\\
          \,\,{\neg}(m\,({\neg}p)\,R)
        \end{pmatrix*}$ \\[1.1em]
        whether  & $(((e \backslash t){\slash_M} t) \backslash (e \backslash t)) \slash t$
        & $\begin{pmatrix*}[l]
          \lambda p\,m\,R.\\
                  \,\, {\neg}(m\,({\neg}p)\,R) \\
          \,\,\,\, +\,{\neg}(m\,p\,R)
        \end{pmatrix*}$\\ \midrule
    \multicolumn{3}{c}{{\bf Complementizers for base form verbs}} \\[\hdrspc]
        that  & $(((e \backslash_V t){\slash_M}t) \backslash (e \backslash_V t)) \slash t$
        & $\begin{pmatrix*}[l]
          \lambda p\,m\,R. \\
          \,\, {\neg}(m\,({\neg}p)\,R)
        \end{pmatrix*}$ \\[1.1em]
        whether & $(((e \backslash_V t){\slash_M} t) \backslash (e \backslash_V t)) \slash t$
        & $\begin{pmatrix*}[l]
          \lambda p\,m\,R.\\
                  \,\, {\neg}(m\,({\neg}p)\,R) \\
          \,\,\,\, +\,{\neg}(m\,p\,R)
        \end{pmatrix*}$ \\
        \bottomrule
      \end{tabular}%%
    \caption{Categorial grammar lexicon. The first column has a word
      form. the second column a categorial type, and third column a
      semantic translation in a language that extends the Epik logical
      language with lambda. The online supplement includes a version
      of this grammar that can be run using Barker and Shan's chart
      parser for categorial grammar \citep{barker2005parser}.}
  \label{lexiconfigure}
\end{figure}

@@

>>>>

\title{Epistemic Semantics in Guarded String Models\thanks{Thanks to Tobias Kappe for insightful reactions to the paper.
Thanks also to three SCiL reviewers for helpful comments.
Earlier versions of the work were presented at in the LUSH talk series at Utrecht in December 2019, and in the Workshop on formal/philosophical/computational approaches to natural language meaning at Rochester in December 2020.  Thanks to the audiences for their reactions.
    .}}
\renewcommand\footnotemark{}
%%\renewcommand\footnoterule{}

@@

\newcommand{\ebackt}{(e \backslash t)}
\begin{figure}[!t]
  \vspace{1em}
  \centering
  \footnotesize
  %% \begin{tabular}[t]{lcc}
  %%   \toprule
  %%       \textsc{Item} & \textsc{Type} & \textsc{Semantics}\\ \midrule
  %%       Amy & $e$ & $\hat{R}_a$\\
  %%       Bob & $e$ & $\hat{R}_b$\\
  %%       it & $d$ & $d$ \\
  %%       heads & $d \backslash_D t$ & $\lambda x.\bullet^*h$ \\
  %%       tails & $d \backslash_D t$ & $\lambda x.\bullet^*t$ \\
  %%       is & $(d \backslash t)\slash(d \backslash_D t)$ & $\lambda P~x.~P~x$ \\
  %%       knows & $(e \backslash t)\slash_M t$ &  $\lambda p~R.~p\vee{\Diamond}_Rp$\\
  %%       believes & $(e \backslash t)\slash_M t$ &  $\lambda p~R.~{\Diamond}_Rp$\\
  %%       that  & $(((e \backslash t){\slash_M}t) \backslash (e \backslash t)) \slash t$
  %%       & $\lambda p\,m\,R.{\neg}(m\,({\neg}p)\,R)$ \\
  %%       whether  & $(((e \backslash t){\slash_M} t) \backslash (e \backslash t)) \slash t$
  %%       & $\lambda p\,m\,R.{\neg}(m\,({\neg}p)\,R)$ \\
  %%       && \multicolumn{1}{r}{$+ {\neg}(m\,p\,R)$} \\ \bottomrule
  %% \end{tabular}

  \newcommand{\hdrspc}{0.3em}
    \begin{tabular}[t]{l>{\hspace{-.8em}}c >{\hspace{-.6em}}c}
    \toprule
    \textsc{Item} & \textsc{Type} & \textsc{Semantics}\\ \midrule
    \multicolumn{3}{c}{{\bf Statives with expletive subject}} \\[\hdrspc]
        heads & $d \backslash_D t$ & $\lambda x.\,\bullet^*h$ \\
        tails & $d \backslash_D t$ & $\lambda x.\,\bullet^*t$ \\ \midrule
    \multicolumn{3}{c}{{\bf Agents}} \\
        Amy & $e$ & $\hat{R}_a$\\
        Bob & $e$ & $\hat{R}_b$\\ \midrule
    \multicolumn{3}{c}{{\bf Auxiliary verbs and expletive subjects}} \\[\hdrspc]
        it & $d$ & {\em{dummy}} \\
        is & $(d \backslash t)\slash(d \backslash_D t)$ & $\lambda P\,x.\,P\,x$ \\
        it's & $(t \slash(d \backslash_D t)$ & $\lambda P\,x.\,P\,x$ \\
        isn't & $t\slash(d \backslash_D t)$ & $\lambda P\,x.\,\neg P\,x$ \\
        doesn't & $(e \backslash t)\slash(d \backslash_V t)$ & $\lambda P\,x.\,\neg P\,x$ \\  \midrule
    \multicolumn{3}{c}{{\bf Tensed attitude verbs}} \\[\hdrspc]
        knows & $(e \backslash t)\slash_M t$ &  $\lambda p\,R.\,p + {\Diamond}_Rp$\\
        believes & $(e \backslash t)\slash_M t$ &  $\lambda p\,R.\,{\Diamond}_Rp$\\ \midrule
    \multicolumn{3}{c}{{\bf Base form attitude verbs}} \\[\hdrspc]
        know & $(e \backslash_V t)\slash_M t$ &  $\lambda p\,R.\,p + {\Diamond}_Rp$\\
        believe & $(e \backslash_V t)\slash_M t$ &  $\lambda p\,R.\,{\Diamond}_Rp$\\ \midrule
    \multicolumn{3}{c}{{\bf Complementizers}} \\[\hdrspc]
        that  & $(((e \backslash t){\slash_M}t) \backslash (e \backslash t)) \slash t$
        & $\begin{pmatrix*}[l]
          \lambda p\,m\,R.\\
          \,\,{\neg}(m\,({\neg}p)\,R)
        \end{pmatrix*}$ \\[1.1em]
        whether  & $(((e \backslash t){\slash_M} t) \backslash (e \backslash t)) \slash t$
        & $\begin{pmatrix*}[l]
          \lambda p\,m\,R.\\
                  \,\, {\neg}(m\,({\neg}p)\,R) \\
          \,\,\,\, +\,{\neg}(m\,p\,R)
        \end{pmatrix*}$\\ \midrule
    \multicolumn{3}{c}{{\bf Complementizers for base form verbs}} \\[\hdrspc]
        that  & $(((e \backslash_V t){\slash_M}t) \backslash (e \backslash_V t)) \slash t$
        & $\begin{pmatrix*}[l]
          \lambda p\,m\,R. \\
          \,\, {\neg}(m\,({\neg}p)\,R)
        \end{pmatrix*}$ \\[1.1em]
        whether & $(((e \backslash_V t){\slash_M} t) \backslash (e \backslash_V t)) \slash t$
        & $\begin{pmatrix*}[l]
          \lambda p\,m\,R.\\
                  \,\, {\neg}(m\,({\neg}p)\,R) \\
          \,\,\,\, +\,{\neg}(m\,p\,R)
        \end{pmatrix*}$ \\ \midrule
        \multicolumn{3}{c}{{\bf Conjunction}} \\[\hdrspc]
        and & $(t \backslash t)\slash t$ &  $\lambda p\,q.\,p \wedge q$\\
        or & $(t \backslash t)\slash t$ &  $\lambda p\,q.\,p + q$\\
        and & $((\ebackt \backslash \ebackt)\slash \ebackt$ &  $\lambda p\,q\,x.\,p(x) \wedge q(x)$\\
        or & $((\ebackt \backslash \ebackt)\slash \ebackt$ &  $\lambda p\,q\,x.\,p(x) + q(x)$\\        
        \bottomrule
      \end{tabular}%% 
    \caption{Categorial grammar lexicon. The first column has a word
      form. the second column a categorial type, and third column a
      semantic translation in a language that extends the Epik logical
      language with lambda. }
  \label{lexiconfigure}
\end{figure}

@@

\clearpage
